{\itshape Advanced Robotics} A simple path optimization method for motion planning

### 2015-10-09 paper.tex
Change table results, introduce partial random shortcut

\articletype{GUIDE}

@@

\begin{abstract}
Most algorithms in probabilistic sampling-based path planning compute 
collision-free paths made of straight line segments lying in the configuration 
space. Due
to the randomness of sampling, the paths make detours that need to be optimized.
The contribution of this paper is to propose a gradient-based algorithm that
transforms a polygonal collision-free path into a shorter one, while both:
\begin{itemize}
\item requiring mainly collision checking, and few time-consuming obstacle 
distance computation,
\item constraining only part of the configuration variables that may cause a 
collision, and not the entire configurations, and
\item reducing parasite motions that are not useful for the problem resolution.
\end{itemize}
The algorithm is simple and requires few parameter tuning. Experimental
results include navigation and manipulation tasks, e.g. an robotic arm 
manipulating throw a window and a PR2 robot working in a kitchen environment, 
and comparisons with a random shortcut optimizer.

@@

For this shortening purpose, random shortcut methods are
still very popular~\cite{Sekhavat-Svestka1998,HauserFastSmooth}. However, random 
shortcut requires fine tuning of the termination condition (see 
Algorithm~\ref{algo:random-shortcut}) and is no efficient due to randomness for long trajectories where only a small part needs to be optimized. Figure~\ref{decoupled_DOF_optimization} presents another situation where random shortcut will always fail to optimize the initial path, since it cannot decouple the robot degrees of freedom (DOF) on which the optimization occurs, contrary to our algorithm.

@@

Some heuristics use random shortcuts on the initial guess combined with a 
trajectory re-building that returns ${C}^1$ shortcuts made of parabolas and lines 
(bang-bang control)~\cite{HauserFastSmooth}. These local refined trajectories 
are time-optimal since they comply with acceleration and velocity constraints. ~\cite{Guernane2011}, also based on random shooting, is guiding configuration-generation with local holonimic considerations. But this method remains only locally optimal, and is not addressing high-DOF problems.
~\cite{Geraerts04clearancebased}, whereas just implemented for freeflyer robots, is using medial axis retractation for clearance and a partial random shortcut (applied only on random DOF) which can address the problem of ~\ref{decoupled_DOF_optimization} but has longer computation time and is not using the information returned by the checker of which links are colliding to guide which DOF to choose for the partial shortcut.

@@

let $W\in\real^{p\times p}$ be a diagonal matrix of weights:
$$
W=\left(\begin{array}{cccccccccc}
w_1 I_{p_1}       &        &  0  \\
    & w_2 I_{p_2} &        &   \\
    &            & \ddots &   \\
  0 &            &        & w_m I_{p_m}
\end{array}\right)
$$
where $I_{p_i}$ is the identity matrix of size $p_i$ and $w_i$ is the weight 
associated to joint $J_i$. We define the length of the straight interpolation 
between two configurations as:
$$
\|\conf_2 - \conf_1\|_{W} \triangleq \sqrt{(\conf_2 - \conf_1)^T W^2 (\conf_2 - 
\conf_1)}.
$$
Weights are used to homogenize translations and rotations in the velocity vector. 
For rotations, the weight is equal to the maximal distance of the robot bodies 
moved by the joint to the center of the joint.

@@

In the collision-configuration $\xx_{i+1}(\tcolli)$, let $\po_c\in \real^3$ be the 
contact point expressed in the global frame ${\cal R}_0$ of each of the two 
bodies. We compute (see Figure~\ref{contact-points}) the associated points $\po_1$ 
and $\po_2$ in the free-configuration $\xx_{i}(\tcolli)$, and thus 
$\mathbf{u}=\po_2-\po_1$.

@@

We denote by $F$ the mapping from $\CS^{wp}$ to $\real$ defined by
\begin{equation}\label{eq:constraint}
F (\xx) =  \mathbf{u}^T \, R^T (\translation^{*} - \translation)
\end{equation}
Note that $F$ vanishes for any path $\xx$ such that in configuration
$\xx(\tcolli)$ the relative position of $\body_2$ w.r.t. $\body_1$ is equal to $
\translation^{*}$ or if the relative position $\translation^{*} - \translation$ is 
orthogonal to $\mathbf{u}$.

@@

Let $q_{k\,i}$ denotes waypoint $k$ along path $x_i$.
The constraint on the position at $t_{coll\,i}$ is a function that depends only
on two waypoints $q_{k\,i}$, $q_{k+1\,i}$, with $0\leq k\leq n$. There exists 
$\beta\in[0,1]$ such that for any $j$:
$$
\xx_j (t_{coll\,i}) = (1-\beta) \conf_{k\,j} + \beta \conf_{k+1\,j}
$$
Therefore, the Jacobian $J_F$ of constraint~(\ref{eq:constraint}) with respect to 
$x$ is
$$
J_F = \left(\begin{array}{cccccc}
0 & \cdots & (1-\beta)\frac{\partial F}{\partial q} (\xx_j(t_{coll\,i})) &
\beta\frac{\partial F}{\partial q} (\xx_j(t_{coll\,i})) & \cdots & 0
\end{array}
\right)
$$
Both $F$ and $\frac{\partial F}{\partial q}$ are provided by our path planning framework~\cite{hpp} as differentiable functions.

@@

@@

In this part we describe the path-optimizer Algorithm~\ref{algo:gradient} 
according to the previous step definitions. The main difficulty here is to handle 
the scalar parameter $\alpha$ determining how much of the computed step $\p$ will 
be traveled through, and also to return a collision-free path. Typically, we 
chose $\alpha_{init} = 0.2$ to process small steps. $\alpha_{init} = 0.5$ is more 
encountered in the optimization literature, procuring larger steps but with more 
risks of collision.

\begin{algorithm}
\begin{algorithmic}%[1] % line numerotation
\Procedure{Optimize}{$\xx_0$}
	\State $\alpha \gets \alpha_{init}$
	\State $minReached \gets false$
	\While{($\textbf{not}(noCollision \textbf{ and } minReached)$)}
		\State $\p = \texttt{computeIterate}()$
		\State $minReached = (||\p||<10^{-3} \textbf{ or } \alpha=1)$
		\State $\xx_1 \gets \xx_0 + \alpha\,\p$
		\If{(\textbf{not}(\texttt{validatePath($\xx_1$)}))}
			\State $noCollision \gets false$
			\If{$(\alpha \neq 1)$}
				\State \texttt{addCollisionConstraints}()
				\State $\alpha \gets 1$
			\Else
				\State $\alpha \gets \alpha_{init}$
			\EndIf
		\Else
			\State $\xx_0 \gets \xx_1$
			\State $noCollision \gets true$
		\EndIf
	\EndWhile
	\Return $\xx_0$
\EndProcedure
\end{algorithmic}
\caption{Gradient-based path-optimization.} \label{algo:gradient}
\end{algorithm}

@@

Figure~\ref{2D_long} illustrates a path example that random shortcut will not manage to 
optimize in an affordable time, because of probabilistically failing to sample 
configurations in the box. Our gradient-based algorithm succeeds to optimize the 
path contained in the box, with the following cost coefficients 
$$
\lambda_{i-1} = \frac{1}{\sqrt{(\conf_{i\,0}-\conf_{i-1\,0})^T \weight^2 
(\conf_{i\,0}-\conf_{i-1\,0})}}
$$
aiming at keeping the same ratio between path segment lengths at 
minimum as at 
initial path, represented by the waypoints ($\conf_{i\,0})_{1\leq i\leq n+1}$.
Without these coefficients, the path that minimizes the cost corresponds to a 
straight line with the waypoints equidistantly allocated, which is not adapted for 
the Figure~\ref{local_box_optim} type of problems with a local passage very
constrained by obstacles. Note that this cost is also working with all other 
examples presented in this paper.

@@

In the included video, we present four situations where our algorithm has been 
% TODO puzzle if included => 5 situations
tested and compared to random shortcut~\cite{randomShortcutHPP}
(Algorithm~\ref{algo:random-shortcut}).
The termination condition of random shortcut allows it to try 
shortening the path until 5 iterations of non-improvement are reached 
(corresponding to $maxNbFailures$ in Algorithm~\ref{algo:random-shortcut}).
%But we admit that restrincting the number of random shortcut iterations is 
%neither a acceptable criterion because of randomness.
%We also discuss the good properties and limits of our algorithm.

% analysis UR2:
On the 5-DOF double-arm problem, one arm has to get around an obstacle while the 
other is relatively far from obstacles. As expected, the initial path given by 
RRT-connect activates both arms to solve the problem. Contrary to random shortcut, 
our optimizer manages to cancel the rotation of the free-arm while optimizing the 
first arm motion. Initial path length 5.17 has been decreased to 4.55 by random shortcut and to 3.20 by the gradient-based optimizer.

% analysis UR5:
For the following example with a 6-axis manipulator arm 
%(Figure~\ref{ur5})
in a  cluttered environment, path reduction only manages to reduce some but not 
all detours. This behavior can be explained by a path over-constraining due to the 
important proximity of the robot to the obstacles during the whole path, and 
because there are not so many DOF to play on to easily avoid collisions and 
return a small-cost solution.
We advance this explanation because on the two following high-DOF examples of the video (and Figure~\ref{pr2_final}), results are better 
in terms of path length and quality.

\begin{figure}[H]
	\centering
	\includegraphics[height=4.9cm,width=1.8cm]{pr2_initial_final_vertical.png}
	\includegraphics[width=5.7cm]{p0_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1RS_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1GB_pr2_alone_merged3.png}\\
	\caption{In this motion planning problem, PR2 robot has just to 
exchange the positions of its arms. The task is simple, however, in absence of 
explicit indication, any probabilistic motion planner will compute a path that 
makes the PR2 mobile basis purposelessly moving. This is the case of RRT-connect 
algorithm (left). Path optimization is expected to remove unnecessary motions. 
The popular random shortcut algorithm fails in this case (middle). Our algorithm 
succeeds (right).}
	\label{pr2_final}
\end{figure}

% analysis PR2 alone:
In the example presented Figure~\ref{pr2_final} and in the video, the mobile 
40-DOF PR2 simply has to cross its arms from 
the left arm up position to the right arm up one. Lengths of the initial path, the 
random shortcut optimized path and the gradient-based optimized path are 
respectively 14.5, 6.34 and 3.62. The RRT-connect planner 
returns detours and activates non-useful DOF such as the head, the torso lift 
and the translation on 
the ground. Once again, random shortcut will hardly optimize the mobile base 
translation of the robot and other unnecessary DOF uses, unlike our 
optimized-path which mainly results in moving the arms as expected 
(Figure~\ref{pr2_final} right).
%The removal 
%of the translation is also a consequence of our cost ponderation as described in 
%the previous section.
% NON ???

% analysis PR2 in kitchen:
We obtain similar results on the PR2 performing a manipulation task 
in a kitchen environment (see the video). The robot has to move 
his hands from the top to the bottom of a table.
Our optimizer manages to reduce the initial length 15.8 from the visibility-PRM 
planner and improves the path quality 
just adding transformation constraints between the table and the 
robot's arms and grippers. Thus, the robot just slightly moves 
backward and uses its arm DOF to avoid the table, instead of 
processing a large motion to get away from the table. With our method, the path length is downed to 4.59, against 8.24 for random shortcut.

Optimization computation time and path length averages are presented for 30 runs of the PR2-crossing-arms in the Table~\ref{tab:results}. In the same way, time computation averages for the PR2-in-kitchen example have been 
calculated: $59.5\,\text{s}$ (gradient-based optimizer) and $76.2\,\text{s}$ (random shortcut).
Thus our method presents 
similar computation times and path lengths for mobile manipulation tasks. However, the extinction of the mobile base motion in the gradient-based optimized path is advanced in the right column of Table~\ref{tab:results}. Thus the problem addressed 
Figure~\ref{decoupled_DOF_optimization} is solved considering this DOF.

\begin{table}[t]
\centering
  \begin{tabular}{cccc}
  \\
  \toprule
     & Computation & Path  & Traveled distance\\
     & time & length & by the base\\
    \midrule
    \midrule
    Initial &  & $13.7$ & $10.9$\\
    Gradient-based & $\,781\text{ms}$ & $3.69$ & $10^{-6}$\\
    Random shortcut & $\,823\text{ms}$ & $3.82$ & $2.94$\\
    \bottomrule
  \end{tabular}
\caption {Results for 30 runs of the PR2-crossing-arms example. For each run, a solution path is planned by Visibility-PRM as initial guess for each optimizer. $\alpha_{init}$ is set to 0.2. The right column represents the distance that is traveled by the robot mobile base during the path.}
\label{tab:results}
\end{table}

@@

The experimental results show that transformation constraints may in some cases be overconstraining. We also tried distance constraints without much success due to the non-continuous differentiability of distance. In a future work, we will study other one-dimensional constraints in order to achieve better results.

>>>>

@@

\begin{abstract}
Most algorithms in probabilistic sampling-based path planning compute 
collision-free paths made of straight line segments lying in the configuration 
space. Due
to the randomness of sampling, the paths make detours that need to be optimized.
The contribution of this paper is to propose a gradient-based (GB) algorithm that
transforms a polygonal collision-free path into a shorter one, while both:
\begin{itemize}
\item requiring mainly collision checking, and few time-consuming obstacle 
distance computation,
\item constraining only part of the configuration variables that may cause a 
collision, and not the entire configurations, and
\item reducing parasite motions that are not useful for the problem resolution.
\end{itemize}
The algorithm is simple and requires few parameter tuning. Experimental
results include navigation and manipulation tasks, e.g. an robotic arm 
manipulating throw a window and a PR2 robot working in a kitchen environment, 
and comparisons with a random shortcut optimizer.

@@

For this shortening purpose, random shortcut (RS) methods are
still very popular~\cite{Sekhavat-Svestka1998,HauserFastSmooth}. However, RS requires fine tuning of the termination condition (see 
Algorithm~\ref{algo:random-shortcut}) and is no efficient due to randomness for long 
trajectories where only a small part needs to be optimized. 
Figure~\ref{decoupled_DOF_optimization} presents another situation where RS will 
always fail to optimize the initial path, since it cannot decouple the 
robot degrees of freedom (DOF) on which the optimization occurs, contrary to our 
algorithm or partial random shortcut (PRS) methods~\cite{Geraerts04clearancebased} that shortcut only one or a group of DOF.

@@

Some heuristics use random shortcuts on the initial guess combined with a 
trajectory re-building that returns ${C}^1$ shortcuts made of parabolas and lines 
(bang-bang control)~\cite{HauserFastSmooth}. These local refined trajectories 
are time-optimal since they comply with acceleration and velocity constraints. 
~\cite{Guernane2011}, also based on random shooting, is guiding configuration-
generation with local holonimic considerations. But this method remains only locally 
optimal, and is not addressing high-DOF problems.
~\cite{Geraerts04clearancebased}, whereas just implemented for freeflyer robots, is 
using medial axis retractation for clearance and a PRS (applied only on random DOF) 
which can address the problem of ~\ref{decoupled_DOF_optimization} but has longer 
computation time and is not using the information returned by the checker of which 
links are colliding to guide which DOF to choose for the PRS.

@@

let $W\in\real^{p\times p}$ be a diagonal matrix of weights:
$$
W=\left(\begin{array}{cccccccccc}
w_1 I_{p_1}       &        &  0  \\
    & w_2 I_{p_2} &        &   \\
    &            & \ddots &   \\
  0 &            &        & w_m I_{p_m}
\end{array}\right)
$$
where $I_{p_i}$ is the identity matrix of size $p_i$ and $w_i$ is the weight 
associated to the lever arm of the joint $J_i$. We define the length of the straight interpolation 
between two configurations as:
$$
\|\conf_2 - \conf_1\|_{W} \triangleq \sqrt{(\conf_2 - \conf_1)^T W^2 (\conf_2 - 
\conf_1)}.
$$
Weights are used to homogenize translations and rotations in the velocity vector. 
For rotations, the weight is equal to the maximal distance of the robot bodies 
moved by the joint to the center of the joint.

@@

In the collision-configuration $\xx_{i+1}(\tcolli)$, let $\po_c\in \real^3$ be the 
contact point expressed in the global frame ${\cal R}_0$ of each of the two 
bodies. We compute (see Figure~\ref{contact-points}) the associated points $\po_1$ 
and $\po_2$ in the free-configuration $\xx_{i}(\tcolli)$, and the difference 
$\mathbf{u}=\po_2-\po_1$ which will be used as the orthogonal direction the bodies can not move along at the path parameter $\tcolli$.

@@

We denote by $F$ the mapping from $\CS^{wp}$ to $\real^3$ defined by
\begin{equation}\label{eq:constraint}
F (\xx) =  R^T (\translation^{*} - \translation)
\end{equation}
Note that $F$ vanishes for any path $\xx$ such that in configuration
$\xx(\tcolli)$ the relative position of $\body_2$ w.r.t. $\body_1$ is equal to $
\translation^{*}$ or if the relative position $\translation^{*} - \translation$ is 
orthogonal to $\mathbf{u}$.

@@

Let $q_{k\,i}$ denotes waypoint $k$ along path $x_i$.
The constraint on the position at $t_{coll\,i}$ is a function that depends only
on two waypoints $q_{k\,i}$, $q_{k+1\,i}$, with $0\leq k\leq n$. There exists 
$\beta\in[0,1]$ such that for any $j$:
$$
\xx_j (t_{coll\,i}) = (1-\beta) \conf_{k\,j} + \beta \conf_{k+1\,j}
$$
Therefore, the Jacobian $J_F$ of constraint~(\ref{eq:constraint}) with respect to 
$x$ is
$$
J_F = \left(\begin{array}{cccccc}
0 & \cdots & (1-\beta)\,\mathbf{u}^T \frac{\partial F}{\partial q} (\xx_j(t_{coll\,i})) & \
\beta\,\mathbf{u}^T \frac{\partial F}{\partial q} (\xx_j(t_{coll\,i})) & \cdots & 0
\end{array}
\right)
$$
Both $F$ and $\frac{\partial F}{\partial q}$ are provided by our path planning framework~\cite{hpp} as differentiable functions.

@@

%The solution step is given by:
%$$
%\mathbf{\pii}^{*} = -V_0(V_0^TH V_0)^{-1}\,V_0^T\nabla c(\xx_i)
%$$
%where $V_0$ is the base of the nullspace of the stack of $J_F$ jacobians.

@@

In this part we describe the GB path-optimizer Algorithm~\ref{algo:gradient} 
according to the previous step definitions. The main difficulty here is to handle 
the scalar parameter $\alpha$ determining how much of the computed step $\p$ will 
be traveled through, and also to return a collision-free path. Typically, we 
chose $\alpha_{init} = 0.2$ to process small steps. $\alpha_{init} = 0.5$ is more 
encountered in the optimization literature, procuring larger steps but with more 
risks of collision.

\begin{algorithm}
\begin{algorithmic}%[1] % line numerotation
\Procedure{Optimize}{$\xx_0$}
	\State $\alpha \gets \alpha_{init}$
	\State $minReached \gets false$
	\While{($\textbf{not}(noCollision \textbf{ and } minReached)$)}
		\State $\p = \texttt{computeIterate}()$
		\State $minReached = (||\p||<10^{-3} \textbf{ or } \alpha=1)$
		\State $\xx_1 \gets \xx_0 + \alpha\,\p$
		\If{(\textbf{not}(\texttt{validatePath($\xx_1$)}))}
			\State $noCollision \gets false$
			\If{$(\alpha \neq 1)$}
				\State \texttt{addCollisionConstraints}()
				\State $\alpha \gets 1$
			\Else
				\State $\alpha \gets \alpha_{init}$
			\EndIf
		\Else
			\State $\xx_0 \gets \xx_1$
			\State $noCollision \gets true$
		\EndIf
	\EndWhile
	\Return $\xx_0$
\EndProcedure
\end{algorithmic}
\caption{Gradient-based (GB) path-optimization.} \label{algo:gradient}
\end{algorithm}

@@

Figure~\ref{2D_long} illustrates a \textit{very long} path example that RS or PRS will not manage to 
optimize in an affordable time, because of probabilistically failing to sample 
configurations in the box. GB succeeds to optimize the 
path contained in the box, with the following cost coefficients 
$$
\lambda_{i-1} = \frac{1}{\sqrt{(\conf_{i\,0}-\conf_{i-1\,0})^T \weight^2 
(\conf_{i\,0}-\conf_{i-1\,0})}}
$$
aiming at keeping the same ratio between path segment lengths at 
minimum as at 
initial path, represented by the waypoints ($\conf_{i\,0})_{1\leq i\leq n+1}$.
Without these coefficients, the path that minimizes the cost corresponds to a 
straight line with the waypoints equidistantly allocated, which is not adapted for 
the Figure~\ref{local_box_optim} type of problems with a local passage very
constrained by obstacles. Note that this cost is also working with all other 
examples presented in this paper.

@@

\begin{figure}[b]
	\centering
	\includegraphics[height=4.9cm,width=1.8cm]{pr2_initial_final_vertical.png}
	\includegraphics[width=5.7cm]{p0_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1RS_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1GB_pr2_alone_merged3.png}\\
	\caption{PR2-crossing-arms example. In this motion planning problem, PR2 robot 
	has just to 
exchange the positions of its arms. The task is simple, however, in absence of 
explicit indication, any probabilistic motion planner will compute a path that 
makes the PR2 mobile basis purposelessly moving. This is the case of RRT-connect 
algorithm (left). Path optimization is expected to remove unnecessary motions. 
The popular RS algorithm fails in this case (middle). Our GB algorithm 
succeeds (right).}
	\label{pr2_final}
\end{figure}

In the included video, we present multiple situations where the GB algorithm has 
been tested and compared to RS~\cite{randomShortcutHPP}
(Algorithm~\ref{algo:random-shortcut}) and PRS ~\cite{partialrandomShortcutHPP} 
adapted from~\cite{Geraerts04clearancebased}.
The termination condition of RS allows it to try 
shortening the path until 5 iterations of non-improvement are reached 
(corresponding to $maxNbFailures$ in Algorithm~\ref{algo:random-shortcut}).
For PRS, first a shortcut is tried on each DOF between $\conf_0$ and $\conf_{n+1}$. Then, for each DOF, configurations are shot as in Algorithm~\ref{algo:random-shortcut} and the steering-method returns a path made by an interpolation on only the current DOF and the previous subpath for other DOF. If this path is collision-free, it is replaced as in RS. This process is also stopped when 5 iterations of non-improvement are reached.

%But we admit that restrincting the number of random shortcut iterations is 
%neither a acceptable criterion because of randomness.
%We also discuss the good properties and limits of our algorithm.

% analysis UR2:
On the double-arm problem (see Figure~\ref{trajectories} top-right), one arm has to get around an obstacle while the 
other is relatively far from obstacles. As expected, the initial path given by 
RRT-connect activates both arms to solve the problem. Contrary to RS, 
GB manages to cancel the rotation of the free-arm while optimizing the 
first arm motion. Initial path length 5.17 has been decreased to 4.55 by RS and to 3.20 by GB.

% analysis UR5:
For the following example with a 6-axis manipulator arm (see Figure~\ref{trajectories} bottom-left)
%(Figure~\ref{ur5})
in a  cluttered environment, path reduction only manages to reduce some but not 
all detours. This behavior can be explained by a path over-constraining due to the 
important proximity of the robot to the obstacles during the whole path, and 
because there are not so many DOF to play on to easily avoid collisions and 
return a small-cost solution.
We advance this explanation because on the two following high-DOF examples of the 
video (and Figure~\ref{pr2_final}), results are better 
in terms of path length and quality.

% analysis PR2 alone:
In the example presented Figure~\ref{pr2_final} and in the video, the mobile 
40-DOF PR2 simply has to cross its arms from 
the left arm up position to the right arm up one. Lengths of the initial path, the 
RS optimized path and the GB optimized path are 
respectively 14.5, 6.34 and 3.62. The RRT-connect planner 
returns detours and activates non-useful DOF such as the head, the torso lift 
and the translation on 
the ground. Once again, RS will hardly optimize the mobile base 
translation of the robot and other unnecessary DOF uses, unlike our 
optimized-path which mainly results in moving the arms as expected 
(Figure~\ref{pr2_final} right).
%The removal 
%of the translation is also a consequence of our cost ponderation as described in 
%the previous section.
% NON ???

% analysis PR2 in kitchen:
We obtain similar results on the PR2 performing a manipulation task 
in a kitchen environment (see the video). The robot has to move 
his hands from the top to the bottom of a table.
Our optimizer manages to reduce the initial length 15.8 from the visibility-PRM 
planner and improves the path quality 
just adding transformation constraints between the table and the 
robot's arms and grippers. Thus, the robot just slightly moves 
backward and uses its arm DOF to avoid the table, instead of 
processing a large motion to get away from the table. With GB, the path length is downed to 4.59, against 8.24 for RS.

Optimization computation time and path length averages are presented for 30 runs of 
the PR2-crossing-arms in the Table~\ref{tab:results}. In the same way, time 
computation averages for the PR2-in-kitchen example have been 
calculated: $59.5\,\text{s}$ (GB) and $76.2\,\text{s}$ (RS).
Thus our method presents 
similar computation times and path lengths for mobile manipulation tasks. However, 
the extinction of the mobile base motion in the gradient-based optimized path is 
advanced in the right column of Table~\ref{tab:results}. Thus the problem addressed 
Figure~\ref{decoupled_DOF_optimization} is solved considering this DOF.

\begin{figure}[t]
	\centering
	\includegraphics[width=7.0cm,height=6.8cm]{pr2_orth_constr_results.png}
	\includegraphics[width=7.0cm,height=6.8cm]{ur2_orth_constr_results.png}\\
	\vspace{0.05cm}
	\includegraphics[width=7.0cm,height=6.3cm]{ur5sph_orth_constr_results.png}
	\includegraphics[width=7.0cm,height=6.3cm]{puzzle_orth_constr_results.png}
	\caption{Trajectories of wrists, end-effectors or center allong different paths: the initial path is represented in red, the RS optimized path in blue and the GB optimized path ($\alpha_{init}=0.1$) in green. For the freeflyer puzzle (bottom right), points $\po_1$, $\po_2$ and vectors $\mathbf{u}$ for constraints computation are also shown in grey and red.}
	\label{trajectories}
\end{figure}

Trajectories results of the robots end-effectors or center are presented 
Figure\ref{trajectories}.

DESCRIBE TRAJECTORIES

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{cccccc}
  \toprule
    \textbf{Problem} & Path obtained from & Computation time  & Path length & Cost & Base traveled distance\\
    \midrule
    \midrule
    & Initial &  & $14.3$ & $ $ &\\
    \textbf{Freeflyer-} & GB & $\,\text{ms}$ & $ $ & $ $ &\\
    \textbf{puzzle} & PRS & $6.53\,\text{ms}$ & $14.3$ & $ $ &\\
    & RS & $68.3\,\text{ms}$ & $6.05$ & $ $ &\\
    \midrule
    & Initial &  & $11.3$ & $ $ &\\
    \textbf{Double-arm} & GB & $318\,\text{ms}$ & $4.95$ & $ $ &\\
    \textbf{5-DOF} & PRS & $8.42\,\text{ms}$ & $8.73$ & $ $ &\\
    & RS & $61.9\,\text{ms}$ & $6.96$ & $ $ &\\
    \midrule
    & Initial &  & $10.8$ & $ $ & $8.03$\,\text{m}\\
    \textbf{PR2-crossing-} & GB & $24.8\,\text{s}$ & $1.90$ & $ $ & $10^{-7}\,\text{m}$\\
    \textbf{arms} & PRS & $41.1\,\text{s}$ & $ 4.73$ & $ $ & $0\,\text{m}$\\
    & RS & $31.5\,\text{s}$ & $1.60$ & $ $ & $2.70\,\text{m}$\\
    \midrule
    & Initial &  & $ $ & $ $ &\\
    \textbf{PR2-in-} & GB & $\,\text{s}$ & $ $ & $ $ &\\
    \textbf{kitchen} & PRS & $\,\text{s}$ & $ $ & $ $ &\\
    & RS & $\,\text{s}$ & $ $ & $ $ &\\
    \midrule
    & Initial &  & $ $ & $ $ &\\
    \textbf{6-DOF-arm-} & GB & $\,\text{s}$ & $ $ & $ $ &\\
    \textbf{with-spheres} & PRS & $\,\text{s}$ & $ $ & $ $ &\\
    & RS & $\,\text{s}$ & $ $ & $ $ &\\
    \midrule
    & Initial &  & $ $ & $ $ &\\
    \textbf{6-DOF-arm-} & GB & $\,\text{s}$ & $ $ & $ $ &\\
    \textbf{through-window} & PRS & $\,\text{s}$ & $  $ & $ $ &\\
    & RS &  $\,\text{s}$ & $ $ & $ $ &\\
    \midrule
    & Initial &  & $19.0$ & $ $ &\\
    \textbf{Baxter-in-} & GB & $2449\,\text{s}$ & $5.85$ & $ $ &\\
    \textbf{office} & PRS & $638\,\text{s}$ & $17.5$ & $ $ &\\
    & RS & $139\,\text{s}$ & $13.3$ & $ $ &\\
    \bottomrule
  \end{tabular}
  }%scalebox
\caption{Average results for 30 runs of several examples presented in the paper or 
the video. For each run, a solution path is planned by Visibility-PRM as initial 
guess for each optimizer. $\alpha_{init}$ is set to 0.1.
For the PR2-crossing-arms example only, the right column represents the 
distance that is traveled by the robot mobile base during the different paths.
}
\label{tab:results}
\end{table}

@@

FUTURE WORK
